Spin canonical rings of log stacky curves

### 2015-07-03 stacky_write_up/spin_cring.tex
added a couple of minor todos at beginning

\todo{Make sure we call all divisors spin canonical divisors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each $\circ$ denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}

>>>>

\todo{Make sure we call all divisors spin canonical divisors}
\todo{Write all block orders as tensors so we don't need to say the $y_i$ preceede the $x_i$.}
\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
\includegraphics{pics/spin-lower-approximations-pic-pics.pdf}
\caption{This figure shows each non-negative best lower approximation of $\frac{14}{5}.$ Each ``$\bullet$'' denotes a best lower approximation and each ``$\circ$'' denotes a lattice point below $5y=14x$ which is not a best lower approximation.  Note that the non-negative best lower approximations generate the monoid of lattice points in the first quadrant satisfying  $5y \le 14x$, with the operation $(a_1, b_1)(a_2, b_2)\mapsto (a_1 + a_2, b_1 + b_2)$ .}\label{fig:s14/5-lattice}
\end{figure}
